CEP Group Meeting

### 2023-07-25 output/presentations/cep_internal_230726/presentation.qmd
Run full pipeline for cortisone for presentation CEP.

---
title: "CEP Group Meeting"
subtitle: "Update on *paper 3* of my PhD"
date: 2023-07-26
author: Lorenzo Fabbri
institute: ISGlobal

format:
  beamer:
    pdf-engine: xelatex
    fontsize: "9pt"
    toc: false
    toc-depth: 2
geometry:
  - left=10mm
  - right=10mm

slide-number: true

bibliography: ../../../../../PhD.bib
link-citations: true
linkcolor: blue

execute:
  echo: false
  warning: false
  error: false
  message: false

editor_options: 
  chunk_output_type: console
---

@@

>>>>

---
title: "CEP Group Meeting"
subtitle: "Update on *paper 3* of my PhD"
date: 2023-07-26
author: Lorenzo Fabbri
institute: ISGlobal
format:
  beamer:
    pdf-engine: xelatex
    fontsize: "9pt"
    toc: false
    toc-depth: 2
geometry:
  - left=10mm
  - right=10mm
slide-number: true
bibliography: ../../../../../PhD.bib
link-citations: true
linkcolor: blue
execute:
  echo: false
  warning: false
  error: false
  message: false
editor_options: 
  chunk_output_type: console
---

@@

- `lmtp` will be the focus of my research stay with ... at ...
